noam_data_exploration_v1

### 2024-08-21 noam_data_exploration_v3.Rmd
Continued troubleshooting issues with log transformed slope. May drop this issue in general. Continued updating models and figures to be at island_side instead of site level, added more effects-style plots.

```{r portfolio effects and synchrony transect level,  fig.height = 8, fig.width = 10}
synchrony_cv_mod <- glmmTMB(cover_cv ~ loreau_synchrony*habitat*island_side + (1|site/transect), 
                             family = Gamma(link = "log"),
                          data = diversity_stability_quadrat, na.action = na.pass)
# model.sel(dredge(synchrony_cv_mod)) # top model by far is as specified
r.squaredGLMM(synchrony_cv_mod) # 0.73, 0.74
summary(synchrony_cv_mod)
emmeans(synchrony_cv_mod, pairwise ~ island_side | habitat, var = "loreau_synchrony", at = list(loreau_synchrony = seq(0,1,0.05)))
synchrony_cv_emm <- emmip(synchrony_cv_mod,
                        habitat ~ loreau_synchrony | island_side,
                        at = list(loreau_synchrony = seq(0,1,0.05)), plotit = F, CIs = T)

>>>>

```{r portfolio effects and synchrony transect level,  fig.height = 8, fig.width = 10}
synchrony_cv_mod <- glmmTMB(cover_cv ~ loreau_synchrony*habitat*island_side + (1|island_side/site/transect), 
                             family = Gamma(link = "log"),
                          data = diversity_stability_quadrat, na.action = na.pass)
# model.sel(dredge(synchrony_cv_mod)) # top model by far is as specified
r.squaredGLMM(synchrony_cv_mod) # 0.78, 0.79
summary(synchrony_cv_mod)
emmeans(synchrony_cv_mod, pairwise ~ island_side | habitat, var = "loreau_synchrony", at = list(loreau_synchrony = seq(0,1,0.05)))
synchrony_cv_emm <- emmip(synchrony_cv_mod,
                        habitat ~ loreau_synchrony | island_side,
                        at = list(loreau_synchrony = seq(0,1,0.05)), plotit = F, CIs = T)
